MCTS Applied to Co-operative Problems

### 2015-08-04 Report/ceec.tex
Dealt with comment on GGP and MCTS

\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually. \gls{ggp} in real time video games is a popular competition \cite{perez2014}

@@

\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}. Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any knowledge about the game itself in order to play.

>>>>

\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually \cite{genesereth2005general}. \gls{ggp} in real time video games is a popular competition \cite{perez2014}

@@

\gls{mcts} \cite{browne2012survey} has been applied to a wealth of domains and is one of the primary algorithms in use for \gls{ggp}\cite{finnsson2008simulation}. Primary advantages are that, when given a sufficient forward model, \gls{mcts} doesn't require any strategic knowledge about the game itself in order to play.
